---
title       : Data Product Pitch
subtitle    : Predicting and visualizing Profits on Fruit over time
author      : Ahsan Ijaz
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Synopsis

1. The purpose of this project is to explore the Fruits data set that comes with Google Visualization library.
2. Google Motion chart is used to provide an interactive display to do so.
3. Prediction using a linear model is made on the profits provided by fruits based on type, time and location of the fruit.

--- 


## Google Motion Visualization
The Google visualization plot is used to check how different variables in the Fruits data set vary with time.
```{r,echo=FALSE,results='asis'}
 Motion=gvisMotionChart(Fruits,timevar = "Year",idvar = "Fruit")
Motion
```

---

## Prediction Mechanism

1. Prediction is done for completion of server calculation requirement and is ill advised.
2. It is ill-advised since the data set is too small and the model too simple.
3. Moreover, the variables used are intentionally chosen as year, type and location so that it throws somewhat ludicrous predictions and also is able to demonstrate the selection of inputs.
4. The model chosen is shown as follows.

```{r,echo=TRUE}
 fit<-lm(Profit~ Location + Fruit + Year,data= Fruits)
fit$coefficients
```

---

## Navigation Bar

A navigation bar is provided that moves from visualization to prediction to help file of the product.

---

## Final Thoughts

1. It is ill advised to take any predictions of the product seriously.
2. The purpose was to learn slidify and shiny apps, and the student in question has gotten some idea of how to use them.



